Defending Against Web Application Attacks: Approaches, Challenges and Implications \vspace{-1mm}

### 2016-07-30 docs/comments/comments.tex
addressed comment 2 of R2

>>>>

\noindent
{\bf Response:}
In our study,
we observed that there are cases where
mechanisms coming from the same category
can be bypassed by similar attack patterns.
This denotes that there are issues
found in the design of each approach.
We also observed that mechanisms which
combine characteristics
from different categories,
could deal with these threats.
This indicates that when solutions
borrow elements from other categories
could be more effective.
Mechanisms can also work together
to defend against different attacks.
For instance,
developers could use {\sc csp}
and \textsc{sql}rand
together to deal with {\sc xss} and
{\sc sql} injection respectively.
We have updated Subsection 7.3
(now named ``Performance Overhead,
Deployment and Security Remarks")
to include all the above remarks.\\

### 2016-07-30 docs/paper/questioning.tex
addressed comment 2 of R2

\begin{figure*}[t]
\begin{center}
\leavevmode
\includegraphics[scale=0.48]{attacks-steps-CSRF.pdf}
\end{center}
\vspace{-5.5mm}
\caption{\label{fig:attacks}Attack model for dynamic and domain specific
language code injection in web applications.
Transitions are labeled with the different attacks that use that path,
while the numbers next to attack labels denote the 
sequence of steps for a particular attack.
Points where different types of defenses
detect or prevent attacks are marked with an `X' symbol:
(1) {\sc ub} (at the browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,
PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08,SSM10,HBBS14,SYMRHKM14,BCJPST15,GLSTMMR12},
(2) {\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
(3) {\sc dbal} (at the database abstraction layer):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05b,SMS13},
(4) {\sc db} (at the database):~\cite{BK04,LLW02,VMV05,CVMA07,GLSTMMR12,CPSPBCCSL12}.}
\vspace{-6mm}
\end{figure*}

@@

{\sc xss-guard}~\cite{BV08} is a training scheme that employs
parse-tree validation. During training, the scheme maps legitimate
scripts to {\sc http} responses. During production {\sc xss-guard}
retrieves for every script included in a response its parsed tree and
checks if it is one of those previously mapped to this response. Apart
from the comparison of the parsed trees, {\sc xss-guard} checks also
for an exact match of lexical entities. To achieve this, the scheme
utilizes that data structures of Firefox's JavaScript engine (Point
{\sc ub}). However, string literals are not compared literally, which
can lead to false negatives. For instance, consider a banner rotator
that every time it runs it creates a value that depends on the
current date and the length of the array that contains the references
of the various images to be displayed. Then, based on this value, it
shows a specific image to a user. In a vulnerable web site that allows
users to post data and contains this banner rotator, a malicious user
could create and store a script that has the same code structure, with
the same JavaScript keywords contained in the rotator script.
%% PL You mean like the rotator?
In this script, attackers could also include references to tiny
images hosted on a web server that is maintained by them in order to
retrieve the {\sc ip} addresses of the users that visit the vulnerable
site.

@@

\subsection{Performance Overhead and Deployment Remarks}

@@

@@

\section*{Author Biographies}
\noindent
{\bf Dimitris Mitropoulos} is a Postdoctoral Researcher
in the Computer Science Department
at Columbia University in the City of New York.
He holds a PhD ('14) in Cyber Security from the
Athens University of Economics and Business.
He is an {\sc ieee} member, a member of SysSec,
and an official writer for the
{\sc xrds}: Crossroads blog of {\sc acm}.
His research interests include application security,
systems security and software engineering.

@@

\noindent
{\bf Michalis Polychronakis} is an Assistant Professor
at Stony Brook University.
He received the B.Sc. ('03), M.Sc. ('05), and Ph.D. ('09)
degrees in Computer Science from the University of Crete, Greece.
% while working as a research assistant in the Distributed
% Computing Systems Lab at {\sc forth-ics}.
Before joining Stony Brook, he was an Associate Research
Scientist at Columbia University in the City of New York.
His research interests include
network and system security and network monitoring and measurement.

\noindent
{\bf Angelos D. Keromytis} is an Associate Professor
of Computer Science at Columbia University in the City
of New York, and the director of the Network Security Lab.
He is currently serving as  Program Manager with the
Information Innovation Office ({\sc i}2O) at the Defense Advanced
Research Projects Agency ({\sc darpa}),
part of the Department of Defense.
His research interests are in systems
and network security,
and cryptography.
He is an {\sc acm} Distinguished Scientist since 2012,
and a founder of Allure Security Technology Inc.

>>>>

\begin{figure*}[t]
\begin{center}
\leavevmode
\includegraphics[scale=0.46]{attacks-steps-CSRF.pdf}
\end{center}
\vspace{-5.5mm}
\caption{\label{fig:attacks}Attack model for dynamic and domain specific
language code injection in web applications.
Transitions are labeled with the different attacks that use that path,
while the numbers next to attack labels denote the 
sequence of steps for a particular attack.
Points where different types of defenses
detect or prevent attacks are marked with an `X' symbol:
(1) {\sc ub} (at the browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,
PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08,SSM10,HBBS14,SYMRHKM14,BCJPST15,GLSTMMR12},
(2) {\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
(3) {\sc dbal} (at the database abstraction layer):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05b,SMS13},
(4) {\sc db} (at the database):~\cite{BK04,LLW02,VMV05,CVMA07,GLSTMMR12,CPSPBCCSL12}.}
\vspace{-6mm}
\end{figure*}

@@

{\sc xss-guard}~\cite{BV08} is a training scheme that employs
parse-tree validation. During training, the scheme maps legitimate
scripts to {\sc http} responses. During production {\sc xss-guard}
retrieves for every script included in a response its parsed tree and
checks if it is one of those previously mapped to this response. Apart
from the comparison of the parsed trees, {\sc xss-guard} checks also
for an exact match of lexical entities. To achieve this, the scheme
utilizes that data structures of Firefox's JavaScript engine (Point
{\sc ub}). However, string literals are not compared literally, which
can lead to false negatives. For instance, consider a banner rotator
that every time it runs it creates a value that depends on the
current date and the length of the array that contains the references
of the various images to be displayed. Then, based on this value, it
shows a specific image to a user. In a vulnerable web site that allows
users to post data and contains this banner rotator, a malicious user
could create and store a script that has the same code structure, with
the same JavaScript keywords contained in the rotator script.
In this script, attackers could also include references to tiny
images hosted on a web server that is maintained by them in order to
retrieve the {\sc ip} addresses of the users that visit the vulnerable
site.

@@

\subsection{\hlc[yellow]{Performance Overhead,
Deployment and Security Remarks}}

@@

\hlc[yellow]{From a security perspective,
we saw that there are cases where
mechanisms coming from the same category
can be bypassed by similar attack patterns.
This denotes that there are issues
found in the design of each approach.
Recall for instance,
that implicit flows can be used against
many taint tracking solutions,
and mimicry attacks can be launched
to bypass training and policy enforcement defenses.
{\sc ifc} mechanisms though,
could deal with such attacks because they
combine characteristics from different categories.
This indicates that when solutions
borrow elements from other categories
could be more effective.
Taking one step further,
we could say that different mechanisms could
be used together to defend different attacks.
For instance,
developers could use {\sc csp}}~\cite{SSM10}
\hlc[yellow]{and \textsc{sql}rand}~\cite{BK04}
\hlc[yellow]{ together
to deal with {\sc xss} and {\sc sql} injection
respectively.}

@@

\section*{Author Biographies}
\noindent
{\bf Dimitris Mitropoulos} is a Postdoctoral Researcher
in the Computer Science Department
at Columbia University.
He holds a PhD ('14) in Cyber Security from the
Athens University of Economics and Business.
His research interests include application security,
systems security and software engineering.

@@

\noindent
{\bf Michalis Polychronakis} is an Assistant Professor
at Stony Brook University.
He received a Ph.D. ('09)
degree in Computer Science from the University of Crete, Greece.
% while working as a research assistant in the Distributed
% Computing Systems Lab at {\sc forth-ics}.
Before joining Stony Brook, he was an Associate Research
Scientist at Columbia University.
His research interests include
network and system security and network monitoring and measurement.

\noindent
{\bf Angelos D. Keromytis} is an Associate Professor
of Computer Science at Columbia University,
and the director of the Network Security Lab.
He is currently serving as  Program Manager with the
Information Innovation Office ({\sc i}2O) at the Defense Advanced
Research Projects Agency ({\sc darpa}),
part of the Department of Defense.
His research interests are in systems
and network security,
and cryptography.
